\chapter{Summary and Outlook}
For the operational phase of \gls{flute}, a stable electron generation will be vital to perform scientific experiments. But also in its current commissioning phase, having a stable electron gun is highly desired. Not only for setting up the beam diagnostic devices, but also for intermediate- and pre-experiments and the comissioning phase of the \gls{linac} section a reliable low energy section is expected.

At the start of the thesis, the stability of the gun was unsatisfactory. As the main source of the instability, the cooling system of the electron gun's body could be identified. But there are other systems and effects that negatively influence the electron generation. These still have not been fully identified and understood, yet.

However this thesis shows that with a control system that interacts with the low power input signal of the klystron, it is possible to improve the stability by creating a closed-loop feedback system using readouts from the \gls{epics} control system as ``sensors'' and a controllable \gls{rf} attenuator in the signal path as ``actuator''. The system transfer function (plant) between the attenuator and the power in the electron gun cavity shows $PT_2$ behavior, so control with a \gls{pid} controller is possible and its positive effects on the stability are shown.

However the studies here also show the limitations of a traditional \gls{lti} control system. The parameterization of the necessary measurement filter is a trade-off between stability of the controller and noise in the system, which in both cases degrades output stability.

The control system could be further optimized by switching to a totally different controller architecture. A possible choice might be model predictive control, which exploits the already identified plant transfer function but determines the output through an optimization process rather than a linear system.

At the moment of writing (June 2021), the \gls{linac} section is under commission, so \gls{flute} is shut down for several weeks. With the \gls{linac} in place and the low energy section operational again, measurements of the electron energies before and after the \gls{linac} can be performed. The method currently used is based on the electron bunch is steered with an electromagnet by the Lorentz force (see \autoref{eq:fl}). By adjusting the electromagnet's coil current in such a way that the electron beam hits a camera screen in the center, the electron energy can be calculated from the coil current. With this destructive and slow process it will be possible to show if the stabilization of the cavity \gls{rf} power actually improves the energies of the accelerated electrons and if the approach using the Faraday cup is an improvement over the cavity \gls{rf} power solution.

The future of the current electron gun and \gls{rf} supply is unclear. Switching to another gun and/or a different \gls{rf} system could lead to an entirely different behavior of the whole system, but the techniques described in this thesis are universally applicable and the control system can easily be modified for usage with different components.