\chapter*{Acknowledgments}\addcontentsline{toc}{chapter}{Acknowledgments}

First I would like to thank Prof. Anke-Susanne Müller and the whole FLUTE team for providing me with the opportunity to write my thesis at their research facility. FLUTE proved to be a one-of-a-kind machine and I really appreciate the work that has already been put into it.

I am very grateful to Prof. Dr.-Ing. John Jelonnek from the Institute for Pulsed Power and Microwave Technology for taking the responsibility of being my first reviewer. Also many thanks to his PhD students Benjamin Ell, Alexander Marek and the others of the team, for listening patiently to my presentations and providing great support in optimizing them. 

I'm especially in debt to my excellent advisor Dr. Nigel John Smale, for always having the time to go over both fundamentals and nifty details of electronics and physics alike. Without his support I wouldn't even be able to switch on FLUTE by now and much less a successful thesis would've been possible.

Valuable inputs from Andreas Böhm regarding the RF attenuator and electronics in general were a great help.

Thanks to Igor Križnar for constructive discussions and programming the graphical user interface and its back-end to control the charge sensitive amplifier.

Construction of the charge sensitive amplifiers connection box by Jürgen Schmid is greatly appreciated.

Thanks to Olena Manzhura from KIT-IPE for her support and for prove-reading the thesis multiple times.

Finally but maybe most importantly, a big thanks goes out to my family, that is my mom Sonja, Stefan and my grandparents Ernst and Gretel. I owe them my deepest appreciation for their support over the last years.
